### 2020-11-09 presentation/1_setting.tex
Rev contribution

% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {System Configuration}
{
\blank [big]
\externalfigure [system.png] [factor=fit]

@@

\I Can we measure less than \m {N_H} times, but recover successfully for most cases?

@@

\I Can we find a basis on which \m {\V {g}} is sparse?
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Literature on Compressive Channel Sensing}
{
\I Bajwa, Haupt, Sayeed, and Nowak (2010): MIMO, linear invariant system, using Dantzig Selector (DS)

@@

\I Lee, Lee, and Yong (2016): MIMO mm-wave, hybrid beamforming, using Orthogonal Matching Pursuit (OMP)
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Question}
{
\I Candès and Tao (2007) proposed a performance bound for DS, then can DS do better than OMP?

\I Does convex programming (DS) trade accuracy with greedy algorithms (OMP)?

\I May we verify a revised performance bound in the concrete case?
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Our Contribution}
{
\I Consider MIMO mm-wave channel, with hybrid beamforming

\I Use a modified DS (convex programming), instead of OMP (greedy algorithm)

\I Illustrate by experiments that DS has better performance

\I Give an analysis of error norm and successful probability in terms of system parameters
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Design of Beamformers}
{
\I We set each entry of \m {\m {F}_B} (resp.\ \m {\m {W}_B}) to be i.i.d.\ complex standard normal, up to a design constant

>>>>

\blank [big, force]

\Title {\TitleText}
\blank [big]

\Subtitle {\AuthorText}
\blank [big]

\Subsubtitle {\InstitutionText}
\Subsubtitle {November 2020}

\page [yes]
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {System Configuration}
{
\blank [big]
\externalfigure [system.png] [factor=fit]

@@

\I Can we measure less than \m {N_H^2} times, but recover successfully for most cases?

@@

\I Can we find a basis on which \m {\V {g}} is sparse?
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Literature on Compressive Sensing}
{
\I Bajwa, Haupt, Sayeed, and Nowak (2010): MIMO, linear invariant system, using Dantzig Selector (DS)

@@

\I Lee, Lee, and Yong (2016): MIMO mm-wave, hybrid beamforming, using Orthogonal Matching Pursuit (OMP)
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Questions}
{
\I How does greedy algorithms (like OMP) trade precision for complexity, and that the opposite is true of convex programs (like DS)?

\I We consider the hybrid system as in Lee, Lee, and Yong (2016), where they proposed an optimal joint design by a nonconvex program, but made considerable approximation.
Is the simplified solution still optimal?

\I Candès and Tao (2007) derived a performance bound for DS.
Does it prove DS to be better?
Does it apply to our case?
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Contribution}
{
\I We demonstrate that the beamformer may serve as the sensing matrix, so DS can be applied.

\I We give a bound (holding for high probability) on expected error norm

\I Numerical results illustrate that in our configuration DS is superior to OMP among other methods, but is achieved at the cost of higher complexity.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Design of Beamformers}
{
\I We set each entry of \m {\m {F}_B} (resp.\ \m {\m {W}_B}) to be i.i.d.\ complex standard normal, up to a design constant

### 2020-11-09 presentation/2_analysis.tex
Rev contribution

\I Should account for the fact that \m {\V {g}} is not strictly sparse

\I Should justify that all four beamformers, \m {\M {F}_B, \M {F}_R, \M {W}_B, \M {W}_R}, have RIP for high probability, thus \m {\m {P}} does too.

\I Should investigate the Big \m {\MC {O}} of error norm by bounding failure events mentioned above.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {The Bound}
{
\I In conclusion, it holds for probability \m {p} that
\Disp {
\NC \VNm {\Hat {\V {g}} - \V {g}} _2
%
\leq \NC 8 \R {L} \RB {\log N_H} ^{3/2} \NR
}
%
\I For design values
\Disp {
\NC N_Y \gtrsim \NC 4 \log N_H, \Q
N_R \gtrsim 16 L \RB {\log N_H}^2 \NR
}
%
\I And it holds that
\Disp {
\NC 1 - p
\lesssim \NC 2 N_H ^{-1/3} \NR
}
%
\I Unfortunately, the values are too big to simulate.
}

>>>>

\I Should consider that \m {\V {g}} is not strictly sparse

\I Should justify that if beamformers, \m {\M {F}_B, \M {F}_R, \M {W}_B, \M {W}_R}, have RIP for high probability, than \m {\m {P}} does too.

\I Should bound the big \m {\MC {O}} of error norm corresponding to these failure events.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {The Bound}
{
\I We argue in the treatise that it holds for probability \m {p} that
\Disp {
\NC \VNm {\Hat {\V {g}} - \V {g}} _2
%
\leq \NC 8 \R {L} \RB {\log N_H} ^{3/2} \NR
}
%
\I For ideal values
\Disp {
\NC N_Y \gtrsim \NC 4 \log N_H, \Q
N_R \gtrsim 16 L \RB {\log N_H}^2 \NR
}
%
\I And it holds that
\Disp {
\NC 1 - p
\lesssim \NC 2 N_H ^{-1/3} \NR
}
%
\I Unfortunately, the values are too big to simulate.
}

### 2020-11-09 presentation/3_simulation.tex
Rev contribution

\I Calculate
\Disp {
\NC \Hat {\V {g}}, \Hat {\V {f}}
\LA \NC \startcases
   \NC \Min {\V {g}', \V {f}'}  \MC \IP {\V {1}, \V {f}'} \NR
   \NC \Rm {subject} \; \Rm {to} \MC \V {g}' \leq \V {f}' \NR
   \NC \MC - \V {g}' \leq \V {f}' \NR
   \NC \MC \M {P}^\Adj \M {P} \V {g}' \leq \M {P}^\Adj \V {y} + \g_{\Ss {DS}} \V {1} \NR
   \NC \MC - \M {P}^\Adj \M {P} \V {g}' \leq - \M {P}^\Adj \V {y} + \g_{\Ss {DS}} \V {1} \NR
\stopcases \NR
}
\I Output \m {\Hat {\M {H}} \LA \M {K} \Rm {vec}^{-1} \SB {\Hat {g}} \M {K}^\Adj}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Performance Metric}
{
\I We call the following quantity \m {\chi} efficiency, which is suggestive of the MIMO channel capacity.

\I Denote \m {\M {E} = \Hat {\M {H}} - \M {H}}.
\Disp {
\NC \chi
= \log \det \SB {\M {I} + \RB {\s + \F {2 \VNm {\M {E}} _2 \VNm {\M {H}} _2} {N_H ^{3/2}}} ^{-1} \M {H} \M {H} ^ \Adj} \NR
}

\I The theoretical efficiency \m {\chi _{\Rm {th}}} is defined by plugging in \m {\V {d}}.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {\m {1/\s} vs \m {\chi}, assorted, \m {N_H=24=2N_Y}}
{
\blank [big]
\externalfigure [assorted-narrow-medium-error.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {\m {1/\s} vs \m {\chi}, assorted, \m {N_H=24=2N_Y}}
{
\blank [big]
\externalfigure [assorted-narrow-very-big-error.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {\m {1/\s} vs \m {\chi}, assorted, \m {N_H=24=3N_Y}}
{
\blank [big]
\externalfigure [assorted-wide-medium-error.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {\m {1/\s} vs \m {\chi}, assorted, \m {N_H=24=3N_Y}}
{
\blank [big]
\externalfigure [assorted-wide-very-big-error.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Time, assorted, \m {N_H=16}}
{
\blank [big]
\externalfigure [assorted-medium-time.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Discussion}
{
\I DS wins other method within the range drawn.

\I Simulated \m {\chi} does not show trend that estimated \m {\T {\chi}} predicts.

\I The weaker constraint on sparsity might have compromised DS's performance.

@@

\I As \m {2N_H^2} grows fast, DS becomes less feasible.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {A Successful Case of Estimation}
{
\blank [big]
\externalfigure [scatter-ddss-success.png] [wfactor=150]

\I Soft thresholding (green) correctly guesses true nonzero components (black), and refines the estimated value (orange)
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {A Failed Case of Estimation}
{
\blank [big]
\externalfigure [scatter-ddss-failure.png] [wfactor=150]

\I Soft thresholding (green) guesses wrong nonzero components (black), and the estimated value (orange) deteriorates
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Complexity}
{
\I The number of Newton steps is about \m {\MC {O} \SB {\VNm {\V {g} _0 - \V {g} ^\star} _1}}, where \m {\VNm {\V {g} _0} _1} is the starting value, \m {\V {g} ^\star} the true value.
Assume that is \m {\MC {O} \SB {\VNm {\M {P} ^\Adj \V {z}} _1}}, or \m {\MC {O} \SB {N_H^2}}.

\I Every Newton step requires a matrix inversion of dimension \m {2 N_H^2}, with complexity \m {\MC {O} \SB {N_H^4}}, giving overall complexity \m {\MC {O} \SB {N_H^6}}.

\I Complexity of Lasso can be similarly argued to be \m {\MC {O} \SB {N_H^6}}.

\I Clearly, OMP has complexity \m {\MC {O} \SB {N_H^2}}, much smaller than DS.
}

>>>>

\I Calculate
\Disp {
\NC \Hat {\V {g}}, \Hat {\V {f}}
\LA \NC \startcases
   \NC \Min {\V {g}', \V {f}'}  \MC \IP {\V {1}, \V {f}'} \NR
   \NC \Rm {subject} \; \Rm {to} \MC \V {g}' \leq \V {f}' \NR
   \NC \MC - \V {g}' \leq \V {f}' \NR
   \NC \MC \M {P}^\Adj \M {P} \V {g}' \leq \M {P}^\Adj \V {y} + \g_{\Ss {DS}} \V {1} \NR
   \NC \MC - \M {P}^\Adj \M {P} \V {g}' \leq - \M {P}^\Adj \V {y} + \g_{\Ss {DS}} \V {1} \NR
\stopcases \NR
}
\I Output \m {\Hat {\M {H}} \LA \M {K} \Rm {vec}^{-1} \SB {\Hat {g}} \M {K}^\Adj}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Performance Metric}
{
\I Let the \m {\T {\chi}}, the relative 2-norm error, be the performance metric.

\Disp {
\NC \T {\chi}
=\NC \RB {
   \F {\log_2 {\VNm {\V {h} -\Hat {\V {h}}} _2}}
   {\log_2 {\VNm {\V {h}}_2}}
} _{\Ss {avg}}, \NR
}

\I Also define \m {\chi} by plugging in \m {\V {d}} into \m {\T {\chi}}.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=16=2N_Y}}
{
\blank [big]
\externalfigure [assorted-narrow-medium-error.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=24=2N_Y}}
{
\blank [big]
\externalfigure [assorted-narrow-very-big-error.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=16=3N_Y}}
{
\blank [big]
\externalfigure [assorted-wide-medium-error.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {\m {1/\s} vs \m {\T {\chi}}, assorted, \m {N_H=24=3N_Y}}
{
\blank [big]
\externalfigure [assorted-wide-very-big-error.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {\It {ibid.}, low signal, assorted, \m {N_H=16=3N_Y}}
{
\blank [big]
\externalfigure [assorted-medium-low-signal-error.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Time, assorted, \m {N_H=16}}
{
\blank [big]
\externalfigure [assorted-medium-time.png] [width=11cm]
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Discussion}
{
\I DS wins other method in the range drawn.

\I \m {\chi} does not show trend that \m {\T {\chi}} predicts.

\I The relaxed sparsity might compromise DS performance

@@

\I As \m {2N_H^2} grows fast, DS becomes less feasible.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {A Successful Case of Estimation}
{
\blank [big]
\externalfigure [scatter-ddss-success.png] [wfactor=180]

\I Soft thresholding (green) correctly guesses true nonzero components (black), and refines the estimated value (orange)
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {A Failed Case of Estimation}
{
\blank [big]
\externalfigure [scatter-ddss-failure.png] [wfactor=180]

\I Soft thresholding (green) guesses wrong nonzero components (black), and the estimated value (orange) deteriorates
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Complexity}
{
\I Let \m {C} denote big-O estimation of complexity, then we argue in the treatise
\Disp {
\NC C_{\Rm {OMP}} =\NC \mathcal {O} \SB {N_H^2 \log N_Y} \NR
\NC C_{\Rm {Lasso}} =\NC \mathcal {O} \SB {N_H^6} \NR
\NC C_{\Rm {DS}} =\NC \mathcal {O} \SB {N_{H}^6} \NR
}

\I Fitting runtime statistics one has
\Disp {
\NC \T {t}_{\Rm {OMP}} \NC \eqsim \mathcal {O} \SB {N_H^{3.6}} \NR
\NC \T {t}_{\Rm {Lasso}} \NC \eqsim \mathcal {O} \SB {N_H^{4.8}} \NR
\NC \T {t}_{\Rm {DS}} \NC \eqsim \mathcal {O} \SB {N_H^{8.3}} \NR
}
}

### 2020-11-09 presentation/4_conclusion.tex
Rev contribution

\Frame {Conclusion}
{
\I We estimate MIMO mm-Wave channel \m {\M {H}} by using a modified DS.

\I We justify DS in present scenario with almost-sparse \m {\V {g}}, and show the RIP of effective beamformer \m {\M {P}}.

\I We propose a error norm analysis of DS in terms of parameters \m {N_H}, \m {N_Y}, and \m{L}, and investigate the asymptotic successful probability.

\I DS may be converted to be a linear program to reduce complexity.

\I While DS does appear superior, it has complexity much greater than OMP.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {References (1/2)}
{
{\tfx
\I A Alkhateeb, O E Ayach, G Leus, R W Heath, \Quote {Channel Estimation and Hybrid Precoding for Millimeter Wave Cellular Systems}, \It {IEEE Journal of Selected Topics in Signal Processing} 8(5), 2014

>>>>

\Frame {Conclusion}
{
\I We estimate MIMO mm-Wave channel \m {\M {H}} by using modifed DS.

\I We justify DS under relaxed sparsity of \m {\V {g}}, and demonstrate the RIP of effective beamformer \m {\M {P}}.

\I We analyze the error norm of DS in terms of \m {N_H}, \m {N_Y}, and \m{L}, and approimate the asymptotic failure probability.

\I By simulation we see that DS can be cast into be a linear program to reduce complexity, and appear to outperform other methods.

\I DS trades off low time and space complexity high precision, and for OMP the opposite is true.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {References (1/2)}
{
{\tfx
\I A Alkhateeb, O E Ayach, G Leus, R W Heath, \Quote {Channel Estimation and Hybrid Precoding for Millimeter Wave Cellular Systems}, \It {IEEE Journal of Selected Topics in Signal Processing} 8(5), 2014

### 2020-11-09 treatise/1_introduction.tex
Rev contribution

From above we note that work on channel estimation seems to favored OMP for its low complexity.
One notable difficulty in channel estimation is that, in the uniform linear array setting, the quantized angle of arrival and departure, which the sensing matrix is based on, does not necessarily match the true ones \cite [GYG18].
Also, as the nature of OMP is greedy, and it is not clear whether it achieves optimality, and the assumption that the channel matrix is sparse warrant justification too.

In this treatise, we suggest DS as an alternative.
Chapter 2 shows, the effective beamformer may serve as the sensing matrix with RIP.
Assuming uniform linear array, the sparsity may be exploited, and a convex program analogous to DS can be used for estimation, which ensures several desirable properties.
In chapter 3, along the lines of \cite [CaT07], we give a bound on expected square error, expressed in terms of the sparsity and the number of paths.
We claim that the bound holds for overwhelming probability.
In chapter 4, we remark that DS can be written as an linear program, for which efficient algorithms are known.
We present numerical results, which show that DS is often superior to OMP among other methods, which is achieved at the cost of higher complexity.

>>>>

We saw that the literature on channel estimation seems to favored OMP for its low complexity.
Then one naturally wonders how greedy algorithms, like OMP, compare to convex programs, like DS.
Can it be that greedy algorithms trade precision for complexity, and that the opposite is true of convex programs?

We consider a hybrid system with uniform linear array as in Lee, Gil, and Lee \cite [LGL16], and aim to compare their result.
Their work proposed an optimal beamformer, jointly designed on both ends via a nonconvex optimization problem, and due to its difficulty they have made considerable approximation.
Is the simplified beamformer still optimal for OMP?
Or will there be mismatch between the angles of sensing matrix and their true values, compromising the algorithm's accuracy?

In this treatise, we illustrate, by the case of uniformly random angles, that DS may outperform OMP among other methods, and the nature of convex program also guarantees its performance.
In chapter 2 we shall see that the effective beamformer may serve as the sensing matrix having RIP for high probability.
The sparsity can be exploited this way, and DS may readily be applied.
In chapter 3, along the lines of Candès and Tao \cite [CaT07], we give a bound (which holds for high probability) on expected error norm, expressed in terms of the suggested sparsity and the number of paths.
In chapter 4, we remark that DS can be cast as a linear program, for which efficient algorithms are known.
Numerical results show that in our configuration DS is superior to OMP among other methods, but is achieved at the cost of higher complexity.

### 2020-11-09 treatise/4_simulation.tex
Rev contribution

Unfortunately, the two-stage method does not always appear to be better than the one-stage method, and we did not include the result in the figures.
It might have something to do with appropriately scaling \m {\g_{\Rm {DS}}} with respect to \m {N_H},
and it is not clear what is most reasonable choice of \m {N_1, N_1, N_2}.

@@

In the assorted plots, DS steadily outperforms other methods.
From lowest to highest error, it usually goes like this: DS, LS, Lasso, OMP.
Though the result is encouraging for our purpose, we wonder why OMP is so bad.
If OMP is even worse than LS, why was it adopted at all, in (say) Lee, Gil, and Lee \cite [LGL16]?
But our configuration may not be comparable to theirs, due to different design of beamformers, so it remains to see how do OMP and DS compare under their settings.

@@

It is not clear, unfortunately, why \m {\T {\chi}} does not agree \m {\chi} (the error bound), and why \m {\chi} does not appear to increase significantly as \m {\s} increases.
As shown above, the \m {\chi} is very constant around 1, thus \m {\T {\chi}} is an overestimation when \m {\s} is high and underestimation when \m {\s} is low.
A possible explanation is that the non-sparsity of \m {\V {g}} undermines the analysis in chapter 3, despite our attempts.
These matters remain to be investigated in the future.

>>>>

Unfortunately, the two-stage method does not always appear to be better than the one-stage method, and we did not include the result in the figures.
It might have something to do with appropriately scaling \m {\g_{\Rm {DS}}} with respect to \m {N_H},
and we do not know what most reasonable choice of \m {N_1, N_1, N_2} is.

@@

In the assorted plots, DS steadily outperforms other methods.
From lowest to highest error, it usually goes like this: DS, LS, Lasso, OMP.
Though the result is encouraging for our purpose, we wonder why OMP is so bad.
Did we make mistakes?
We do not think so.
A crucial reason might be that in Lee, Gil, and Lee \cite [LGL16], the angles of departure and arrival is distributed within a cluster of standard deviation 15 degrees, and in ours, they are uniform on the unit circle.
One is then tempted to say, we suggested a low complexity beamformer and high complexity estimation method, while they suggested a high complexity beamformer and low complexity estimation method, and the low complexity solution does not seem effective in our settings.
It remains to see, however, how OMP and DS compare, if done exactly under their settings.

@@

We are not sure either, unfortunately, why \m {\T {\chi}} does not agree \m {\chi} (the error bound), and why \m {\chi} does not appear to increase significantly as \m {\s} increases.
As shown above, the \m {\chi} is very constant around 1, thus \m {\T {\chi}} is an overestimation when \m {\s} is high and underestimation when \m {\s} is low.
A possible explanation is that the non-sparsity of \m {\V {g}} undermines the analysis in chapter 3, despite our attempts.
These matters remain to be investigated in the future.

### 2020-11-09 treatise/5_conclusion.tex
Rev contribution

One must be careful in giving meaningful comparison of existent analytic bounds for compressive sensing algorithms, as they might work in different settings.
Indeed, DS requires a RIP matrix and performance is guaranteed in noisy observation \cite [CaT07], while RIP is not easily to justify rigorously, and its easy construction is even an open problem.
OMP, on the other hand, requires only an entrywise i.i.d.\ Normal sensing matrix \cite [TrG07a], but much analysis remains to be done.
OMP trades off precision for a lower time and space complexity, and for DS the other way around, and this eloquently illustrates that different technique suits different problems and constraints, as is true in every discipline of engineering.

>>>>

One must be careful in giving meaningful comparison of existent analytic bounds for compressive sensing algorithms, as they might work in different settings.
Indeed, DS requires a RIP matrix and performance is guaranteed in noisy observation \cite [CaT07], while RIP is not easily to justify rigorously, and its easy construction is even an open problem.
OMP, on the other hand, may require only an entrywise i.i.d.\ sensing matrix \cite [TrG07a], but much of its property remains open.
On the whole, DS trades off low time and space complexity high precision, and for OMP the opposite is true.
